---
title: "Gapminder Data Observations"
author: "Carolyn Wright"
output: rmdformats::material
#output: html_document
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

```{r,echo=FALSE}

#Include source files in the RMD. Note: echo = FALSE so that the code will not be displayed in the RMD file.
source(file = "Wrangling_code.R", echo = FALSE)
source(file = "Visualization_function.R", echo = FALSE)

```
---

---
---


<h3> Brief Data Description </h3>
 + Female Children out of school are the number of primary-school-age female children not enrolled in primary or secondary school
 + Total fertility rate. The number of children that would be born to each woman with prevailing age-specific fertility rates

---

<h3> Plot Descriptions </h3>
 + Top Left: Histogram of average fertility rate by continent between two years
 + Top Right: Histogram of average number of female children that are out of school by continent between two years
 + Bottom Left: Spaghetti chart of average fertility rate by continent between two years.
 + Bottom Right: Spaghetti chart of average number of female children that are out of school by continent between two years.
 
<div align="center"><h1><b> Set 1: 1900 - 2000 <b></div> </h1>
```{r,echo=FALSE,out.width="100%"}
#the following code will output histograms and spaghetti plots for all years included in the dataset

Visualization_years(Full_GapMinder_Data,1900, 2000,1,1)

```


---
<div align="center"><h1><b>Set 2: 2000 - 2021</b> </div> </h1>
```{r,echo=FALSE,out.width="100%"}
#the following code will output histograms and spaghetti plots for all years included in the dataset

Visualization_years(Full_GapMinder_Data,2000, 2021,1,1)

```

<h3>Observations:</h3>
